### 2017-04-13 paper/oopsla17-submission/intro2.tex
asd

\mypara{Challenge 1: Acquiring Labeled Programs}
%
The first challenge for supervised learning
is to acquire a corpus of training data, here,
a set of ill-typed programs \emph{labeled}
with the exact sub-terms that are the actual
cause of the type error.
%
Prior work has often enlisted expert users
to manually judge ill-typed programs and
determine the ``correct'' fix \citep[\eg][]{Loncaric2016-uk},
but this approach does not scale well to
a dataset large enough to support machine
learning.
%
Worse, while expert users have intimate
knowledge of the type system, they may
have a blind spot with regards to the
kinds of mistakes novices make, and
cannot know in general what novice users
intended to do.

Our \emph{first contribution} \autoref{sec:overview}
is a set of more than 4,500 labeled programs,
gives us an accurate ground truth of
the kinds of errors and the (locations
of the) fixes that novices make in
practice.
%
We obtain this set by observing that
software development is an iterative
process and programmers eventually
fix their own ill-typed programs,
perhaps after multiple incorrect
exploratory attempts.
%
To exploit this observation we instrumented
the \ocaml compiler to collect fine-grained
traces of student interactions over two instances
of an undergraduate Programming Languages course at
%
\begin{anonsuppress}
UC San Diego (IRB \#140608).
\end{anonsuppress}
\begin{noanonsuppress}
AUTHOR's INSTITUTION (IRB HIDDEN).
\end{noanonsuppress}
%
We can then post-process the resulting time-series
of programs submitted to the \ocaml compiler into
a set of pairs of ill-typed programs and their
\emph{fixed} versions, the \emph{first} (type-)correct
program in the trace suffix.
%
We obtain the location labels by computing a
\emph{tree-diff} between the two terms to find
the exact sub-terms that were changed in the fix.

@@

Our \emph{third contribution} \autoref{sec:evaluation}
is a systematic evaluation of our data-driven approach
using different classes of features like the above, and
with three different classification algorithms: linear
classifiers, decision forests and deep neural networks.
%
Our evaluation lets us identify the best features and
classifier and empirically characterize the importance
of different features for error localization.
%
In particular, we find that while machine learning
on its own performs slightly worse than existing
purely constraint based approaches (\eg \ocaml, \sherrloc),
once we augment the data with feature abstraction
corresponding to the \emph{type error slice} \cite{Tip2001-qp},
the resulting classifier significantly outperforms
state-of-the-art by 18 percentage points.

>>>>

\mypara{Challenge 1: Acquiring Labeled Programs}
%
The first challenge for supervised learning
is to acquire a corpus of training data, here,
a set of ill-typed programs \emph{labeled}
with the exact sub-terms that are the actual
cause of the type error.
%
Prior work has often enlisted expert users
to manually judge ill-typed programs and
determine the ``correct'' fix \citep[\eg][]{Loncaric2016-uk},
but this approach does not scale well to
a dataset large enough to support machine
learning.
%
Worse, while expert users have intimate
knowledge of the type system, they may
have a blind spot with regards to the
kinds of mistakes novices make, and
cannot know in general what novice users
intended.

Our \emph{first contribution} (\autoref{sec:overview})
is a set of more than 4,500 labeled programs,
gives us an accurate ground truth of
the kinds of errors and the (locations
of the) fixes that novices make in
practice.
%
We obtain this set by observing that
software development is an iterative
process and programmers eventually
fix their own ill-typed programs,
perhaps after multiple incorrect
exploratory attempts.
%
To exploit this observation we instrumented
the \ocaml compiler to collect fine-grained
traces of student interactions over two instances
of an undergraduate Programming Languages course at
%
\begin{anonsuppress}
UC San Diego (IRB \#140608).
\end{anonsuppress}
\begin{noanonsuppress}
AUTHOR's INSTITUTION (IRB HIDDEN).
\end{noanonsuppress}
%
We can then post-process the resulting time-series
of programs submitted to the \ocaml compiler into
a set of pairs of ill-typed programs and their
\emph{fixed} versions, the \emph{first} (type-)correct
program in the trace suffix.
%
We obtain the location labels by computing a
\emph{tree-diff} between the two terms to find
the exact sub-terms that were changed in the fix.

@@

Our \emph{third contribution} (\autoref{sec:evaluation})
is a systematic evaluation of our data-driven approach
using different classes of features like the above, and
with three different classification algorithms: linear
classifiers, decision forests and deep neural networks.
%
Our evaluation lets us identify the best features and
classifier and empirically characterize the importance
of different features for error localization.
%
In particular, we find that while machine learning
on its own performs slightly worse than existing
purely constraint based approaches (\eg \ocaml, \sherrloc),
once we augment the data with feature abstraction
corresponding to the \emph{type error slice} \cite{Tip2001-qp},
the resulting classifier significantly outperforms
state-of-the-art by 18 percentage points.
